greta.Rmd

### 2019-08-06 notebook/ghost-fit.Rmd
full ensemble

# Model
mean <- x_t + r * x_t * (1 - x_t / K) - a * x_t ^ Q / (x_t ^ Q + H ^ Q)
distribution(x_t1) <- normal(mean, sigma)
m <- model(a)
```

@@

```{r}
mean <- x_t + r * x_t * (1 - x_t / K) - a * x_t ^ Q / (x_t ^ Q + H ^ Q)
distribution(x_t1) <- normal(mean, sigma * x_t)
m <- model(a)
```

@@

## Random sample

```{r}

random <- sample(unique(data$reps), 1)
wide <- data %>% 
  filter(reps %in% random) %>%
  spread(reps, x) %>%
  select(-t) %>% 
  as.matrix()
n <- dim(wide)[1]

@@

```{r}
mean <- x_t + r * x_t * (1 - x_t / K) - a * x_t ^ Q / (x_t ^ Q + H ^ Q)
distribution(x_t1) <- normal(mean, sigma)
m <- model(a)
```

```{r }
system.time({
  draws3 <- mcmc(m, n_samples = 1000, warmup = 3000, chains = 4, verbose = FALSE)
})
```

@@

>>>>

# Model
mean <- x_t + r * x_t * (1 - x_t / K) - a * x_t ^ Q / (x_t ^ Q + H ^ Q)
distribution(x_t1) <- normal(mean, sigma * x_t)
m <- model(a)
```

@@

```{r}
a <- uniform(0, 1)
mean <- x_t + r * x_t * (1 - x_t / K) - a * x_t ^ Q / (x_t ^ Q + H ^ Q)
distribution(x_t1) <- normal(mean, sigma * x_t)
m <- model(a)
```

@@

## Full ensemble

```{r}
wide <- data %>% 
  spread(reps, x) %>%
  select(-t) %>% 
  as.matrix()
n <- dim(wide)[1]

@@

```{r}
a <- uniform(0, 1)
mean <- x_t + r * x_t * (1 - x_t / K) - a * x_t ^ Q / (x_t ^ Q + H ^ Q)
distribution(x_t1) <- normal(mean, sigma * x_t)
m <- model(a)
```

```{r }
system.time({
  draws3 <- mcmc(m, n_samples = 1000, warmup = 3000, chains = 6, verbose = FALSE)
})
```

@@

```{r }
p <- list(r = .05, K = 2, Q = 5, H = .38, sigma = .02, a=0.023, N = 4e3, x0 = 0.2, N = 1e4)
source("../R/ghost.R")
p$a <- 0.021
tf <- theory(p) %>% mutate(a = 0.021)

p$a <- 0.023
tf <- theory(p) %>% mutate(a = 0.023) %>% bind_rows(tf)

p$a <- 0.024
tf <- theory(p) %>% mutate(a = 0.024) %>% bind_rows(tf)

tf <- tf %>% mutate(a = as.factor(a))

tf %>%
  ggplot(aes(x, potential, col=a)) +
  geom_line(lwd=1)
